An Airdrop That Preserves Recipient Privacy

### 2019-01-18 paper/defs.tex
first cut at security definitions

TODO: Need to state security properties formally: 
(1) $c$ and $\text{sig}$ should reveal nothing about $\PK$,
(2) without $\SK$ we have existential unforgeability under a 
(one-time) chosen message attack.

>>>>

\rsw{Needs improved typesetting, notation} PAD must satisfy two security properties:

\paragraph{Privacy}
The privacy game
\RSW{notation for game naming}
is defined as follows:

\begin{itemize}
\item Adversary sends $\msg$ and keys $(\PK_0, \SK_0)$, $(\PK_1, \SK_1)$ to Challenger.

\item Challenger chooses $b \rgets \{0,1\}$,
computes $(c, s) \gets \text{sendTokens}(\PK_b)$ and
$\sig \gets \text{sign}(\SK_b, (c, s), \msg)$,
and sends $(c, \sig)$ to Adversary.

\item Adversary outputs $b'$.

\end{itemize}
An airdrop scheme is \emph{private} if $\sizeof{\probab{b' = b} - \nicefrac{1}{2}} < \text{negl}$.

\paragraph{Existential unforgeability}
The existential forgery game is defined as follows:

\begin{itemize}
\item Challenger chooses a key $(\PK, \SK)$ and sends $\PK$ to Adversary.

\item Adversary computes $(c, s) \gets \text{sendTokens}(\PK)$, chooses \msg, sends $(c, s, \msg)$ to Challenger.

\item Challenger computes $\sig \gets \text{sign}(\SK, (c, s), \msg)$ and sends to Adversary.

\item Adversary outputs $(\msg', \sig')$.

\end{itemize}
An airdop is \emph{existentially unforgeable} if
$\probab{\msg' \neq \msg \wedge \text{verify}(c, \msg', \sig') = \text{yes}} < \text{negl}$.

%TODO: Need to state security properties formally: 
%(1) $c$ and $\text{sig}$ should reveal nothing about $\PK$,
%(2) without $\SK$ we have existential unforgeability under a 
%(one-time) chosen message attack.
